### 2018-12-06 draft.tex
first go at refs

Matings between sufficiently diverged populations or species produce low fitness hybrids, or fail altogether, due to the action of intrinsic incompatibilities(\citealt{dobzhansky1937}, citealt{muller1942}) or ecological barriers \textcolor{red}{(Schluter 1998)}. %YANIV DOUBLE CHECK THIS REFERENCE IS ABOUT ECOLOGICAL BARRIERS
  Misallocated reproductive effort spent on producing low fitness hybrids can be prevented through natural selection favoring prezygotic barriers, a process known as reinforcement \citep{Dobzhansky1937,Servedio:2003dw}.
Reinforcement is generally conceptualized as the evolution of an assortative mating locus (felsenstein1981) or female preference locus (servedioANDkirkpatrick).   
Both reinforcement mechanisms assume males and females have a shared interest in preventing the production of low-fitness hybrid offspring. 
However, reproductive interactions are generally more fractious than this, as the costs of reproductive effort can differ by sex and reproductive stage (ranging from gamete formation to mating itself) (arnqvistandrowebook).  
Because male and female interests are not always aligned, interspecific sexual conflict over the hybridization rate (parkerANDpatridge) may create an often overlooked hurdle to the evolution of reinforcement.   
We develop a population genetic model of interspecific sexual conflict and show that it prevents the long term maintenance of reinforcement.  
We suggest that interspecific sexual conflict may be particularly severe after mating, hampering the reinforcement of postmating-prezygotic reproductive isolating barriers.

SENTENCE ABOUT REINFORCEMENT IN SYMPATRY
The process of reinforcement has gained widespread acceptance due to theoretical models showing its plausibility (CITE), lab experiments showing its evolution (CITE), and correlative studies showing its signature (CITE).  
The most compelling cases of reinforcement involve premating barriers. 
In addition to Coyne and Orr's () and other () demonstrations of enhanced behavioral isolation of sympatric Drosophila species, the reinforcement of premating barriers has been documented in numerous taxa, including damselflies (Waage 1975, 1979), Hawaiian crickets (Otte 1989), frogs (Blair 1974, Littlejohn and Loftus-Hill 1968, Hobel and Gerhardt 2003,?), fish (Rundle and Schluter 1998), birds? (Ratcliffe and Grant 1983b), Saetre et al (1997), and plants (Hopkins). %YOU WROTE: "Newer refs? These look old/classic. I have not read them all.. wonder if they show reinforcement or reproductive character displacement" I AM GOING TO LEAVE THIS FOR YOU YANIV

$MOVE TO END OF FIRST PARAGRAPH? MORE PREMATING VS POSTMATING SETUP
While standard theory does not differentiate between the reinforcement of premating  and postmating-prezygotic [i.e. gametic] barriers, ``bona fide cases of reinforcement and of gametic isolation are still rare" (Turissini et al 2017). %YANIV CAN YOU CHECK THIS QUOTE?
In fact, we know of only two unequivocal cases. 
First, the wild gingers species,  \textit{Costus scaber}, preferentially rejects  \textit{C. pulverulentus} pollen when the populations are sympatric, but not when they are allopatric (Kay and Schemske (2008)).  %pollen-pistil incompatibility, postmating prezygotic
Second, the extent of gametic isolation between \textit{Drosophila yakuba} females and \textit{D. santomea} males is stronger for sympatric than allopatric \textit{D. yakuba} samples  (Matute (2010)). 
Counter to these two examples, comparative surveys in both \textit{Drosophila} (Turissini et al 2017) and plants \citep{Moyle et al 2004} fail to find a broad signature of reinforcement of postmating-prezygotic barriers. 
There are few other plausible cases of postmating-prezygotic reinforcement in maize (cite), sea urchins (Lessios, 2007, Palumbi and Lessios 2005; Vacquier and Swanson 2011), and mussels (Slaughter et al 2008), however, these appear to involve barriers that are ineffective (Slaughter et al 2008) and/or reflect the action of selection on intraspecific matings (CITE).

Interspecific sexual conflict could explain the difference in the frequency of reinforcement of premating and postmating-prezygotic barriers.   
Sexual conflict arises when different reproductive strategies maximize the fitness of each sex.    
 Sexual conflict in interspecific reproductive interactions can occur when the sexes `disagree' on the optimal hybridization rates \citep{Parker:1998bx}.  
The extent of this disagreement will reflect sex-specific differences in the trade-off between intraspecific and interspecific reproductive success, but is likely to be more intense for postmating barriers.
Consider the fate of a sperm (or pollen grain) in the reproductive tract of a heterospecific female. 
Without sperm limitation and with nonzero hybrid fitness, male fitness will increase and female fitness will decrease when sperm fertilize heterospecific eggs.   
In this case, selection will favor mechanisms by which male gametes overcome postmating barriers in females of other species, preventing reinforcement and breaking down reproductive isolation between species.   
By contrast, the reinforcement of pre-mating barriers may involve less conflict, because a trait preferred by conspecifics is disfavored by heterospecifics.   
Of course this distinction is not absolute --  the extent of sexual conflict will depend on how mechanistic details of premating and postmating interactions mediate the  sex-specific tradeoff between inter- and intraspecific reproductive success.

The possibility of an interspecific sexual conflict over hybridization has been pointed out previously \citet{Parker:1998bx}, and has since been discussed briefly by \citet{Gavrilets:2005gl} and Coyne and Orr (1998).  
\citet{Parker:1998bx} modeled sexual conflict as an evolutionary game between males and females where the costs of searching for a mate could be outweighed by the benefits of siring a low fitness hybrid. 
Their model clearly highlights the potential for a sexual conflict over reinforcement, but it does not include any explicit genetics.  We therefore do not know how this conflict affects the co-evolution of male traits and female preferences, the impacts of this conflict on patterns of introgression, and the broader genomic consequences of such conflict and its resolution.

@@

We show that sexual conflict can erode reinforced interspecific isolating barriers. 
Ever since Felsenstein (CITE) identified that recombination presents  a fundamental challenge to the reinforcement of reproductive isolation, a large body of theory has aimed to identify how and when reinforcement could evolve (CITE  LOADS). 
Consequently, the identification of further theoretical challenges to the evolution of reinforcement has lagged (but see Servedio for an important counterexample).

Despite, or perhaps because of, its role in hampering speciation, sexual conflict over hybridization has received little attention in the literature \citep[but see ][]{Parker1998, Parker and Partridge, Gavrilets}.  
% since the idea was first proposed in a game theoretic framework twenty years ago \citep{Parker1998}. 
%While previous work \citep{Parker1998, Gavrilets2014} highlighted the possibility of interspecific sexual conflict and speculated on its macroevolutionary consequences, it did not generate the population genetic predictions necessary to identify if such a conflict has occurred or is occurring. 
Our population genetic analysis shows the transient dynamics generated by sexual conflict over reinforcement and the genetic signatures it leaves behind. 
The results provide a rich set of predictions and interpretations of empirical patterns that were missed by previous game theoretic \citep{parkerpartridge, gavrilets} and verbal \citep{Coyne} descriptions of the potential for such conflicts. 
We show that interspecific sexual conflict favors male gametic traits that overcome heterospecific female barriers. 
Beleaguered by interspecific sexual conflict, the break down of reproductive isolation is marked by the rapid adaptive introgression of male compatibility factors, followed by the slow homogenization of the frequency of female barriers across species. 
By contrast, in the absence of such conflict, species-specific compatibility alleles  cross species boundaries under a more restricted set of parameters.
Ultimately, we show that barriers acting at different stages of hybridization can affect how reinforcement proceeds.
%The rate and pattern of introgression in models with and without sexual conflict depends on the strength of other evolutionary forces. \textcolor{red}{say instead: no sexual conflict, results no different than classic reinforcement model?}
%We show that barriers acting at different stages of hybridization can affect how reinforcement proceeds.

@@

We believe that sexual conflict over reinforcement is more likely for postmating than for premating barriers. 
However, this mapping is not absolute and will depend on details of the biological system.   
%\textcolor{red}{That is, there are likely scenarios in which the fitness benefit of siring a low-fitness hybrid outweighs the opportunity cost of a heterospecific mating opportunity \cite{Parkerpartidge}.}  \textcolor{blue}{Take for example, flowering time, if the survival of maladaptive hybrids outweighs the fitness cost of shedding pollen on days when heterospecific, but not conspecific styles are receptive, selection will favor extending  male flowering  time.} \textcolor{red}{YANIV I DON'T UNDERSTAND THIS SENTENCE} \textcolor{blue}{did this example help? I like this sentence and think it's important.}
That is, certain physical and/or biochemical properties of postmating interactions can minimize the opportunity for interspecific sexual conflict by enforcing a trade-off between overcoming a heterospecific barrier and successfully fertilizing conspecifics.    
For example, if pollen must travel far enough, but not too far, down the style to achieve fertilization \citep[as observed in interspecific crosses in Nicotiana ][]{Lee2008}, pollen will not be able to simultaneously succeed on both inter- and intra- specific styles.
This will minimize the opportunity for interspecific sexual conflict.  
Indeed, a change in style length appears to underlie the evolution of reinforcement in a sympatric \textit{Silene} species pair \citep{Nista2015}.  
More directly, in competitive fertilization, factors modulating intraspecific gamete precedence provide mechanisms by which the reinforcement of postmating-prezygotic barriers may stably evolve \citep{Howard199,Lorch2007}.   
As such, the observation that conspecific sperm precedence is reinforced in sympatric populations of \citep{Drosophila pseudoobscura}  and \citep{D. persimilis} \citep{Castillo_biorXiv} is broadly consistent with our theory.

@@

\paragraph{Comparison to previous models:}  
The mechanism of assortative mating is a major distinguishing feature of our reinforcement model. 
In our model, a female expressed isolating barrier requires a male expressed compatibility allele to overcome it.   % yb deleted (whether postmating-prezygotic or premating)
Introgression of this male compatibility allele is facilitated by the fact that it does not prevent mating with conspecifics. 
This \textit{lock/key} model of reproductive isolation was inspired by the mechanism underlying well-understood cases of postmating isolation (CITE maize/teo, sea urchin, and abalone). 
For example, pollen-style (in)compatibilities between \textit{Zea mays} subspecies are controlled by pairs of loci known as gametophytic factors, for which stylar rejection phenotypes are overcome by the expression of pollen compatibility alleles at a tightly linked locus \cite{NELSON,1993}. 
%, including the gametophytic factor system in \emph{Z. maize} spp. (CITE), the bindin/EBR1 system in sea urchins (CITE), and the lysin/VERL system (CITE) in abalone. 
By contrast, previous reinforcement models incorporating separate sexes typically treat the sexes interchangeably \citep[e.g. ][]{Felsenstein}, or assume assortative mating by a female preferences for diverged male traits (Lande PNAS, Servedio and Kirkpatrick 1997, Kelly and Noor... others?). 
These \textit{preference/trait} models implicitly induce a trade-off between interspecific and intraspecific mating --a male with a trait favored by heterospecific females will have limited mating success with conspecifics. 
As such, while \textit{lock/key} type of mating interactions can result in the transient -- and ultimately failed -- reinforcement of postmating-prezygotic isolation, this outcome does not arise in \textit{preference/trait}  type models.%  \textcolor{red}{SHOULD WE MENTION COSTUS SPP.?} \textcolor{blue}{ NOOOOOO}

@@

The role of sexual conflict in removing species boundaries runs counter to the conventional role sexual conflict is thought to play in speciation  \citep[][]{GavriletsWaxman,RiceandHistert,ParkerPartrdige}. 
Previous theory \citep{GavriletsWaxman} and experiments \citep{Rice1996Nature} suggested that sexually antagonistic coevolution can lead to coevolutionary arms races in each incipient species, pleiotropically resulting in behavioral or mechanical isolation. 
In this manner \emph{intraspecific} sexual conflict was thought to be an "Engine of Speciation" \citep[e.g. ][]{RiceandHistert}.  
In contrast, interspecific sexual conflict hampers speciation by preventing the evolution of reinforcement, despite both types of conflict (intra- and interspecific) arising from male propensity to mate and female propensity to resist certain matings.

We are not the first to show that sexual selection can act to  bring species together, rather than pushing them apart. 
Recently, Servedio and Burger's (2015) found that Fisherian sexual selection can undermine the evolution of assortative mating.
They showed that when female preference can introgress across  species backgrounds, they can favour heterospecific male traits by sexual selection even when such traits are disfavored by natural selection.   
By  providing a mating advantage to maladaptive male traits, this model undermines the evolution of reinforcement.  
In some areas of parameter space, our pre-mating model shows that the preference introgresses faster than the trait and then selects for spread of the species-specific compatibility allele, replicating the finding of Servedio and Burger (2015).  \textcolor{red}{Is this true? STILL WORKING ON FIGURING THIS OUT}  
However, the dynamics of our postmating model reveal a much different story -- a sperm's ability to overcome a reproductive barrier adaptively introgresses across species' boundaries, while the barrier allele is disfavored, and can only cross species boundaries once the sperm trait is common. \

@@

We show that sexual conflict can result in the transient evolution of reinforcement.  
Specifically, we expect the transient reinforcement of \textit{lock and key} postmating prezygotic barriers in which males do not trade off inter- and intraspecific mating success.  
This major result -- that is, that postmating prezygotic barriers are rarely stably reinforced,  can explain numerous empirical  observations.  
Most straightforwardly, our result is consistent with the finding that postmating prezygotic isolation does not differ between sympatric and allopatric species pairs across three angiosperm genera (Moyle et al), suggesting that these barriers are not reinforced among sympatric species.
Additionally, our findings are compatible with the growing consensus that, contrary to initial claims, reinforcement does not drive the evolution of sperm-egg interactions underlying reproductive barriers in broadcast spawners (Lessios, 2007; \textcolor{red}{Palumbi and Lessios 2005; Vacquier and Swanson 2011}).

Most immediately, our model provides a clear interpretation and novel predictions concerning patterns of geographic variation at loci underlying cross compatibility between \text{Zea mays} subspecies. 
These `Gametophytic Factors' consist of tightly linked alleles in which stylar barriers require pollen signal for effective pollination \citep{Things}, a mechanism  that inspired our modeling approach.   %The evolution of gametophytic factors in \textit{Zea mays spp.} provide an opportunity for refined tests of our theory. 
As predicted by standard models of reinforcement, styles of  the wild teosinte, \textit{Z. m. mexicana}, grown near \textit{Z. m. mays} landraces, reject most maize pollen. 
However, ``[t]he  unexpected  presence  of  the [male compatibility] allele in sympatric landrace maize appear[ed]... to negate  any  effect  of  [the] crossing  barrier" puzzling researchers \citep{medyca paper}.   %YANIV I DON"T THINK YOU NEED TO QUOTE THIS
Our model predicts that adaptive introgression of the teosinte allele is responsible for the compatibility of sympatric \textit{Zea m. mays} / \textit{Z. m. mexicana} populations.  
Isolating and sequencing compatibility haplotypes in these maize landraces will provide a strong test of our theory.

Our results highlight an under-appreciated challenge to the reinforcement of postmating-prezygotic barriers. 
However, rather than negating our theory, cases in which  postmating-prezygotic barriers are reinforced provide a strong opportunity to further test our theory.  
We predict that cases in which postmating prezygotic isolation is reinforced should (1) be transient, (2)  entail a trade-off between male success in overcoming  inter and intraspecific postmating barriers and/or (3) involved unidirectional gene flow. 
As such, the few documented cases in which postmating-prezygotic barriers are reinforced (without conspecific gamete precedence) are of particular interest to our theory.   
We know of two such cases. 
Kay \citep{Kay and Schemske, Yost and Kay}, demonstrated that post-pollination barriers are reinforced in a pair of wild gingers. 
Importantly, however, gene flow in this species-pair is unidirectional, negating any sexual conflict over reinforcement. \textcolor{red}{Ali do we have a graph showing this?} %YANIV.. SHOWING WHAT? 
Matute (2010) convincingly found that \textit{Drosophila yakuba} females from populations sympatric with \textit{D. santomea},show elevated gametic isolation from \textit{D. santomea}, but show no evidence for conspecific sperm precedence. 
Our theory provides the strong prediction that swapping \textit{D. yakuba} male compatibility alleles into  \textit{D. santomea} males will result in less effective intraspecific matings. % I THINK THEY MAY HAVE A UNIDIRECTINAL THING GOING TOO
Thus, in addition to making sense of known observations, our model provides novel research directions.  
In sum, our work explains the paucity of well-established cases of the reinforcement of postmating prezygotic barriers, and generates specific testable predictions when these barriers appear to be reinforced.

@@

For ease of analysis and interpretation, we made numerous additional assumptions in our reinforcement models of both pre- and postmating barriers.  
For example, we modeled postzygotic isolation by assuming that hybrids are not well adapted to either parental species' habitat (e.g., Schluter 1998), rather than assuming intrinsic hybrid incompatibility arising from a single underdominant locus or two locus Dobzhansky-Muller interactions.  
We further assumed a relatively simple basis of local (mal)adaptation -- each prezygotic incompatibility was linked to one local adaptation locus, and fitness was multiplicative both within and among locally (mal)adaptive loci. 
%and that populations exited in two simple demes rather than e.g. a more complex cline.  
Future empirical work should aim to identify model systems in which to test our hypothesis, and novel theory, involving the relaxation of these assumptions, should be tailored to the biologically-inspired scenarios investigated.

@@

\newpage
\bibliography{speciationLibrary}
\bibliographystyle{amnatnat}

>>>>

Matings between sufficiently diverged populations or species produce low fitness hybrids, or fail altogether, due to the action of intrinsic incompatibilities \citep{dobzhansky1937, muller1942} or ecological barriers \citep{schluter1998}. %YANIV DOUBLE CHECK THIS REFERENCE IS ABOUT ECOLOGICAL BARRIERS
Misallocated reproductive effort spent on producing low fitness hybrids can be prevented through natural selection favoring prezygotic barriers, a process known as reinforcement \citep{dobzhansky1937, servedio2003}.
Reinforcement is generally conceptualized as the evolution of an assortative mating locus \citep{felsenstein1981} or female preference locus \citep{servedio1997}.   
Both reinforcement mechanisms assume males and females have a shared interest in preventing the production of low-fitness hybrid offspring. 
However, reproductive interactions are generally more fractious than this, as the costs of reproductive effort can differ by sex and reproductive stage (ranging from gamete formation to mating itself) \citep{arnqvistandrowebook}.  
Because male and female interests are not always aligned, interspecific sexual conflict over the hybridization rate \citep{parker1998}  may create an often overlooked hurdle to the evolution of reinforcement.   
We develop a population genetic model of interspecific sexual conflict and show that it prevents the long term maintenance of reinforcement.  
We suggest that interspecific sexual conflict may be particularly severe after mating, hampering the reinforcement of postmating-prezygotic reproductive isolating barriers.

SENTENCE ABOUT REINFORCEMENT IN SYMPATRY
The process of reinforcement has gained widespread acceptance due to theoretical models showing its plausibility (CITE), lab experiments showing its evolution (CITE), and correlative studies showing its signature (CITE).  
The most compelling cases of reinforcement involve premating barriers. 
In addition to Coyne and Orr's \citeyearpar{coyneandorrbook} and other \citeyearpar{coyneandorr1989, coyneandorr1997} demonstrations of enhanced behavioral isolation of sympatric Drosophila species, the reinforcement of premating barriers has been documented in numerous taxa, including damselflies \citep{waage1979},  frogs \citep{blair1974, littlejohn1968, hobel2003}, fish \citep{rundle1998}, birds \citep{ratcliffe1983,saetre1997}, and plants \citep{hopkins2013}. %YOU WROTE: "Newer refs? These look old/classic. I have not read them all.. wonder if they show reinforcement or reproductive character displacement" I AM GOING TO LEAVE THIS FOR YOU YANIV

% MOVE TO END OF FIRST PARAGRAPH? MORE PREMATING VS POSTMATING SETUP 
While standard theory does not differentiate between the reinforcement of premating  and postmating-prezygotic [i.e. gametic] barriers, ``bona fide cases of reinforcement and of gametic isolation are still rare'' \citep{turissini2018}. %YANIV CAN YOU CHECK THIS QUOTE?
In fact, we know of only two unequivocal cases. 
First, the wild gingers species,  \textit{Costus scaber}, preferentially rejects  \textit{C. pulverulentus} pollen when the populations are sympatric, but not when they are allopatric \citep{kay2008}.  %pollen-pistil incompatibility, postmating prezygotic
Second, the extent of gametic isolation between \textit{Drosophila yakuba} females and \textit{D. santomea} males is stronger for sympatric than allopatric \textit{D. yakuba} samples \citep{matute2010}. 
Counter to these two examples, comparative surveys in both \textit{Drosophila} \citep{turissini2018} and plants \citep{moyle2004} fail to find a broad signature of reinforcement of postmating-prezygotic barriers. 
There are few other plausible cases of postmating-prezygotic reinforcement in maize \citep{kermicle2006}, sea urchins \citep{lessios2007,geyer2003,zigler2003}, and mussels \citep{slaughter2008}, however, these appear to involve barriers that are ineffective \citep{slaughter2008} and/or reflect the action of selection on intraspecific matings \citep{geyer2009}.

Interspecific sexual conflict could explain the difference in the frequency of reinforcement of premating and postmating-prezygotic barriers.   
Sexual conflict arises when different reproductive strategies maximize the fitness of each sex.    
 Sexual conflict in interspecific reproductive interactions can occur when the sexes `disagree' on the optimal hybridization rates \citep{parker1998}.  
The extent of this disagreement will reflect sex-specific differences in the trade-off between intraspecific and interspecific reproductive success, but is likely to be more intense for postmating barriers.
Consider the fate of a sperm (or pollen grain) in the reproductive tract of a heterospecific female. 
Without sperm limitation and with nonzero hybrid fitness, male fitness will increase and female fitness will decrease when sperm fertilize heterospecific eggs.   
In this case, selection will favor mechanisms by which male gametes overcome postmating barriers in females of other species, preventing reinforcement and breaking down reproductive isolation between species.   
By contrast, the reinforcement of pre-mating barriers may involve less conflict, because a trait preferred by conspecifics is disfavored by heterospecifics.   
Of course this distinction is not absolute --  the extent of sexual conflict will depend on how mechanistic details of premating and postmating interactions mediate the  sex-specific tradeoff between inter- and intraspecific reproductive success.

The possibility of an interspecific sexual conflict over hybridization has been pointed out previously \citet{parker1998}, and has since been discussed briefly by \citet{gavrilets2005} and \citet{coyneandorrbook}.  
\citep{parker1998} modeled sexual conflict as an evolutionary game between males and females where the costs of searching for a mate could be outweighed by the benefits of siring a low fitness hybrid. 
Their model clearly highlights the potential for a sexual conflict over reinforcement, but it does not include any explicit genetics.  We therefore do not know how this conflict affects the co-evolution of male traits and female preferences, the impacts of this conflict on patterns of introgression, and the broader genomic consequences of such conflict and its resolution.

@@

We show that sexual conflict can erode reinforced interspecific isolating barriers. 
Ever since \citet{felsenstein1981} identified that recombination presents  a fundamental challenge to the reinforcement of reproductive isolation, a large body of theory has aimed to identify how and when reinforcement could evolve (CITE  LOADS). 
Consequently, the identification of further theoretical challenges to the evolution of reinforcement has lagged (but see \citet{}Servedio for an important counterexample).

Despite, or perhaps because of, its role in hampering speciation, sexual conflict over hybridization has received little attention in the literature \citep[but see ][]{parker1998, gavrilets2005, gavrilets2014}.  
% since the idea was first proposed in a game theoretic framework twenty years ago \citep{Parker1998}. 
%While previous work \citep{Parker1998, Gavrilets2014} highlighted the possibility of interspecific sexual conflict and speculated on its macroevolutionary consequences, it did not generate the population genetic predictions necessary to identify if such a conflict has occurred or is occurring. 
Our population genetic analysis shows the transient dynamics generated by sexual conflict over reinforcement and the genetic signatures it leaves behind. 
The results provide a rich set of predictions and interpretations of empirical patterns that were missed by previous game theoretic \citep{parker1998, gavrilets2005} and verbal \citep{coyneandorrbook} descriptions of the potential for such conflicts. 
We show that interspecific sexual conflict favors male gametic traits that overcome heterospecific female barriers. 
Beleaguered by interspecific sexual conflict, the break down of reproductive isolation is marked by the rapid adaptive introgression of male compatibility factors, followed by the slow homogenization of the frequency of female barriers across species. 
By contrast, in the absence of such conflict, species-specific compatibility alleles  cross species boundaries under a more restricted set of parameters.
Ultimately, we show that barriers acting at different stages of hybridization can affect how reinforcement proceeds.
%The rate and pattern of introgression in models with and without sexual conflict depends on the strength of other evolutionary forces. \textcolor{red}{say instead: no sexual conflict, results no different than classic reinforcement model?}
%We show that barriers acting at different stages of hybridization can affect how reinforcement proceeds.

@@

We believe that sexual conflict over reinforcement is more likely for postmating than for premating barriers. 
However, this mapping is not absolute and will depend on details of the biological system.   
%\textcolor{red}{That is, there are likely scenarios in which the fitness benefit of siring a low-fitness hybrid outweighs the opportunity cost of a heterospecific mating opportunity \cite{Parkerpartidge}.}  \textcolor{blue}{Take for example, flowering time, if the survival of maladaptive hybrids outweighs the fitness cost of shedding pollen on days when heterospecific, but not conspecific styles are receptive, selection will favor extending  male flowering  time.} \textcolor{red}{YANIV I DON'T UNDERSTAND THIS SENTENCE} \textcolor{blue}{did this example help? I like this sentence and think it's important.}
That is, certain physical and/or biochemical properties of postmating interactions can minimize the opportunity for interspecific sexual conflict by enforcing a trade-off between overcoming a heterospecific barrier and successfully fertilizing conspecifics.    
For example, if pollen must travel far enough, but not too far, down the style to achieve fertilization \citep[as observed in interspecific crosses in Nicotiana ][]{lee2008}, pollen will not be able to simultaneously succeed on both inter- and intra- specific styles.
This will minimize the opportunity for interspecific sexual conflict.  
Indeed, a change in style length appears to underlie the evolution of reinforcement in a sympatric \textit{Silene} species pair \citep{nista2015}.  
More directly, in competitive fertilization, factors modulating intraspecific gamete precedence provide mechanisms by which the reinforcement of postmating-prezygotic barriers may stably evolve \citep{howard1993,lorch2007}.   
As such, the observation that conspecific sperm precedence is reinforced in sympatric populations of \citep{Drosophila pseudoobscura}  and \citep{D. persimilis} \citep{castillo2018} is broadly consistent with our theory.

@@

\paragraph{Comparison to previous models:}  
The mechanism of assortative mating is a major distinguishing feature of our reinforcement model. 
In our model, a female expressed isolating barrier requires a male expressed compatibility allele to overcome it.   % yb deleted (whether postmating-prezygotic or premating)
Introgression of this male compatibility allele is facilitated by the fact that it does not prevent mating with conspecifics. 
This \textit{lock/key} model of reproductive isolation was inspired by the mechanism underlying well-understood cases of postmating isolation (CITE maize/teo, sea urchin, and abalone). 
For example, pollen-style (in)compatibilities between \textit{Zea mays} subspecies are controlled by pairs of loci known as gametophytic factors, for which stylar rejection phenotypes are overcome by the expression of pollen compatibility alleles at a tightly linked locus \citep{nelson1994}. 
%, including the gametophytic factor system in \emph{Z. maize} spp. (CITE), the bindin/EBR1 system in sea urchins (CITE), and the lysin/VERL system (CITE) in abalone. 
By contrast, previous reinforcement models incorporating separate sexes typically treat the sexes interchangeably \citep[e.g. ][]{felsenstein1981}, or assume assortative mating by a female preferences for diverged male traits \citep{lande1981, servedio1997, kelly1996}(Lande PNAS, Servedio and Kirkpatrick 1997, Kelly and Noor... others?). 
These \textit{preference/trait} models implicitly induce a trade-off between interspecific and intraspecific mating --a male with a trait favored by heterospecific females will have limited mating success with conspecifics. 
As such, while \textit{lock/key} type of mating interactions can result in the transient -- and ultimately failed -- reinforcement of postmating-prezygotic isolation, this outcome does not arise in \textit{preference/trait}  type models.%  \textcolor{red}{SHOULD WE MENTION COSTUS SPP.?} \textcolor{blue}{ NOOOOOO}

@@

The role of sexual conflict in removing species boundaries runs counter to the conventional role sexual conflict is thought to play in speciation  \citep{parker1998, gavrilets2002, rice2005}. 
Previous theory \citep{gavrilets2002} and experiments \citep{rice1996} suggested that sexually antagonistic coevolution can lead to coevolutionary arms races in each incipient species, pleiotropically resulting in behavioral or mechanical isolation. 
In this manner \emph{intraspecific} sexual conflict was thought to be an "Engine of Speciation" \citep[e.g. ][]{rice2005}.  
In contrast, interspecific sexual conflict hampers speciation by preventing the evolution of reinforcement, despite both types of conflict (intra- and interspecific) arising from male propensity to mate and female propensity to resist certain matings.

We are not the first to show that sexual selection can act to  bring species together, rather than pushing them apart. 
Recently, \citet{servedio2014}  found that Fisherian sexual selection can undermine the evolution of assortative mating.
They showed that when female preference can introgress across  species backgrounds, they can favour heterospecific male traits by sexual selection even when such traits are disfavored by natural selection.   
By  providing a mating advantage to maladaptive male traits, this model undermines the evolution of reinforcement.  
In some areas of parameter space, our pre-mating model shows that the preference introgresses faster than the trait and then selects for spread of the species-specific compatibility allele, replicating the finding of \citet{servedio2014}.  \textcolor{red}{Is this true? STILL WORKING ON FIGURING THIS OUT}  
However, the dynamics of our postmating model reveal a much different story -- a sperm's ability to overcome a reproductive barrier adaptively introgresses across species' boundaries, while the barrier allele is disfavored, and can only cross species boundaries once the sperm trait is common. \

@@

We show that sexual conflict can result in the transient evolution of reinforcement.  
Specifically, we expect the transient reinforcement of \textit{lock and key} postmating prezygotic barriers in which males do not trade off inter- and intraspecific mating success.  
This major result -- that is, that postmating prezygotic barriers are rarely stably reinforced,  can explain numerous empirical  observations.  
Most straightforwardly, our result is consistent with the finding that postmating prezygotic isolation does not differ between sympatric and allopatric species pairs across three angiosperm genera \citep{moyle2004}, suggesting that these barriers are not reinforced among sympatric species.
Additionally, our findings are compatible with the growing consensus that, contrary to initial claims, reinforcement does not drive the evolution of sperm-egg interactions underlying reproductive barriers in broadcast spawners \citep[see discussion in ][]{vacquier2011}.

Most immediately, our model provides a clear interpretation and novel predictions concerning patterns of geographic variation at loci underlying cross compatibility between \text{Zea mays} subspecies. 
These `Gametophytic Factors' consist of tightly linked alleles in which stylar barriers require pollen signal for effective pollination \citep{Things}, a mechanism  that inspired our modeling approach.   %The evolution of gametophytic factors in \textit{Zea mays spp.} provide an opportunity for refined tests of our theory. 
As predicted by standard models of reinforcement, styles of  the wild teosinte, \textit{Z. m. mexicana}, grown near \textit{Z. m. mays} landraces, reject most maize pollen. 
However, ``[t]he  unexpected  presence  of  the [male compatibility] allele in sympatric landrace maize appear[ed]... to negate  any  effect  of  [the] crossing  barrier" puzzling researchers \citep{kermicle2006}.   %YANIV I DON"T THINK YOU NEED TO QUOTE THIS
Our model predicts that adaptive introgression of the teosinte allele is responsible for the compatibility of sympatric \textit{Zea m. mays} / \textit{Z. m. mexicana} populations.  
Isolating and sequencing compatibility haplotypes in these maize landraces will provide a strong test of our theory.

Our results highlight an under-appreciated challenge to the reinforcement of postmating-prezygotic barriers. 
However, rather than negating our theory, cases in which  postmating-prezygotic barriers are reinforced provide a strong opportunity to further test our theory.  
We predict that cases in which postmating prezygotic isolation is reinforced should (1) be transient, (2)  entail a trade-off between male success in overcoming  inter and intraspecific postmating barriers and/or (3) involved unidirectional gene flow. 
As such, the few documented cases in which postmating-prezygotic barriers are reinforced (without conspecific gamete precedence) are of particular interest to our theory.   
We know of two such cases. 
Kay \citep{kay2008, yost2009}, demonstrated that post-pollination barriers are reinforced in a pair of wild gingers. 
Importantly, however, gene flow in this species-pair is unidirectional, negating any sexual conflict over reinforcement. \textcolor{red}{Ali do we have a graph showing this?} %YANIV.. SHOWING WHAT? 
\citet{matute2010} convincingly found that \textit{Drosophila yakuba} females from populations sympatric with \textit{D. santomea},show elevated gametic isolation from \textit{D. santomea}, but show no evidence for conspecific sperm precedence. 
Our theory provides the strong prediction that swapping \textit{D. yakuba} male compatibility alleles into  \textit{D. santomea} males will result in less effective intraspecific matings. % I THINK THEY MAY HAVE A UNIDIRECTINAL THING GOING TOO
Thus, in addition to making sense of known observations, our model provides novel research directions.  
In sum, our work explains the paucity of well-established cases of the reinforcement of postmating prezygotic barriers, and generates specific testable predictions when these barriers appear to be reinforced.

@@

For ease of analysis and interpretation, we made numerous additional assumptions in our reinforcement models of both pre- and postmating barriers.  
For example, we modeled postzygotic isolation by assuming that hybrids are not well adapted to either parental species' habitat \citep[a.g. ][]{schluter1998}, rather than assuming intrinsic hybrid incompatibility arising from a single underdominant locus or two locus Dobzhansky-Muller interactions.  
We further assumed a relatively simple basis of local (mal)adaptation -- each prezygotic incompatibility was linked to one local adaptation locus, and fitness was multiplicative both within and among locally (mal)adaptive loci. 
%and that populations exited in two simple demes rather than e.g. a more complex cline.  
Future empirical work should aim to identify model systems in which to test our hypothesis, and novel theory, involving the relaxation of these assumptions, should be tailored to the biologically-inspired scenarios investigated.

@@

\newpage
\bibliographystyle{unsrtnat}
\bibliography{gfrefs.bib}
